An IFS study of Low-powered Radio Galaxies

### 2018-01-16 paper.tex
EoDC:
Futher work on paper.

 On branch master
 Changes to be committed:
	new file:   KDC_size_age.png
	new file:   Mg_sigma.png
	modified:   paper.tex

	\begin{table*}
		% \centering
	% \begin{threeparttable}
		\caption{Key sample characteristics of the Southern Sample galaxies. Col.\,1: host galaxy name. Col.\,2: radio source name from Parkes Southern Radio Source Catalogue. We hereafter refer to the last galaxy by its PKS name only. Col.\,3: redshift. Col.\,4: National Radio Astronomy Observatory (NRAO) Very Large Array (VLA) Sky Survey (NVSS) 1.4 GHz flux density \citep{Condon1998}. Col.\,5: Two Micron All Sky Survey (2MASS) $K$-band apparent magnitude (with errors of $\pm 0.025$ mag; \citealt{Skrutskie2006}). Col.\,6: dust morphologies from (a) \citet{Govoni2000}, (b) \citet{Lauer2005}, (c) \citet{Bettoni2001}, (d) \citet{Sandage1979}, (e) \citet{Colbert2001}.}
		\label{tab:sample}
		\begin{tabular}{l c c c c l}
			\hline
			\hline
			Host galaxy	& Radio source 	& Redshift	& $S_\text{1.4\,GHz}$	& $m_K$ & Dust morphology\\
						& (PKS) 		& 			& (mJy) 			& (mag)	&\\
			\hline 
			ESO 443-G024 & 1258-321 	& 0.01703	& $1387 \pm 45$		& 8.51 & no dust\tnote{a}	\\ 
			IC 1459 	& 2254-367 		& 0.00565 	& $1280 \pm 45$		& 6.81 & dust lane\tnote{b}	\\
			IC 1531 	& 0007-325 		& 0.02553 	& \leavevmode\phantom{0}$388 \pm 12$		& 9.55 & --					\\
			IC 4296		& 1333-\leavevmode\phantom{0}33 		& 0.01248 	& $1342 \pm 41$		& 7.50 & edge-on disc\tnote{b} \\
			NGC 612 	& 0131-\leavevmode\phantom{0}36 		& 0.02954 	& \leavevmode\phantom{0}$585 \pm 18$		& 9.58 & dust lane\tnote{c}	\\
			NGC 1316 	& 0320-\leavevmode\phantom{0}37 & 0.00591 	& \leavevmode\phantom{0}$255 \pm 10$		& 5.59 & dust patches\tnote{b} \\
			NGC 1399 	& 0336-\leavevmode\phantom{0}35 & 0.00472 	& \leavevmode\phantom{0}$209 \pm \leavevmode\phantom{0}7$	& 6.31 & no dust\tnote{b}	\\
			NGC 3100 	& 0958-314 		& 0.00879 	& \leavevmode\phantom{0}$530 \pm 16$		& 8.08 & dust lane\tnote{d}	\\
			NGC 3557 	& 1107-372 		& 0.01016 	& \leavevmode\phantom{0}$484 \pm 16$		& 7.20 & face-on disc\tnote{b}\\
			NGC 7075 	& 2128-388 		& 0.01819 	& \leavevmode\phantom{0}$837 \pm 28$		& 9.56 & --					\\
			--			& 0718-\leavevmode\phantom{0}34 		& 0.02897 	& $1119 \pm 41$		& 9.97 & dust patches\tnote{e} \\
			\hline
			\hline
		\end{tabular}
	% 	\begin{tablenotes}
	% 	\footnotesize
	% 	\note Col.\,1: host galaxy name. Col.\,2: radio source name from Parkes Southern Radio Source Catalogue. Col.\,3: redshift. Col.\,4: National Radio Astronomy Observatory (NRAO) Very Large Array (VLA) Sky Survey (NVSS) 1.4 GHz flux density \citep{Condon1998}. Col.\,5: Two Micron All Sky Survey (2MASS) $K$-band apparent magnitude (with errors of $\pm 0.025$ mag; \citealt{Skrutskie2006}). Col.\,6: dust morphologies from (a) \citet{Govoni2000}, (b) \citet{Lauer2005}, (c) \citet{Bettoni2001}, (d) \citet{Sandage1979}, (e) \citet{Colbert2001}. 
	% 	\item We hereafter refer to the last galaxy by its PKS name only.
	% 	\end{tablenotes}
	% \end{threeparttable}
	\end{table*}

@@

	\subsection{Stellar Kinematics}
		\label{subsec:starKin}
		Each bin is fit independently again using \textsc{pPXF} with the MILES library. For the fit regions around potential emission lines are masked, and a fourth order polynomial additive continuum correction is used. A Monte--Carlo (MC) estimate of the uncertainties is used.

	\subsection{Ionized Gas Distribution and Kinematics}
		\label{subsec:EmissionLines}
		We fit the ionized gas fluxes and kinematics from the emission lines listed in Table \ref{tab:EmissionLine}, using Gaussian templates are used to independently fit emission lines from the interstellar medium (ISM), with a single LOSVDs, independently of the stellar kinematics. However, to minimize template mismatch, whereby emission lines are erroneously fitted to the edges of badly modeled and thus subtracted absorption features, we follow the method set out in \citet{Sarzi2005}, whereby the stellar component is first fitted as above with masked potential emission line regions, followed by the unmasking and fitting of the [\ion{O}{iii}] doublet which sets the kinematics for all the emission lines and finally the amplitude of the remaining emission lines. Some of the forbidden emission lines have the ratio of their amplitudes fixed (see Table \ref{tab:EmissionLine}, Col.\,4).

		\begin{table}
	 		% \centering
	 	% \begin{threeparttable}
	 		\caption{Emission lines considered in the \textsc{pPXF} fits. Col\,1: Emission line name. Col\,2: Emission line rest-frame wavelength. Col\,3: Doublet rest-frame wavelength for forbidden lines. Col\,4: The fixed ratio of the amplitudes of the lines within a doublet. `Free' indicates the amplitudes of both doublet constituents are fit independently of each other.}
	 		\label{tab:EmissionLine}
	 		\begin{tabular}{l c c c}
	 		\hline
	 		\hline
	 		Emission & Rest-frame & Doublet rest-frame & Amplitude  \\
	 		Line & wavelength & wavelength & ratio \\
	 		 & (\AA) & (\AA) \\
	 		\hline
	 		\bracket{\ion{O}{ii}} 	& 3726.03 & 3728.82 & Free \\
	 		H\,$\delta$ 	& 4101.76 & -- & -- \\
	 		H\,$\gamma$ 	& 4340.47 & -- & -- \\
	 		H\,$\beta$ 		& 4861.33 & -- & -- \\
	 		\bracket{\ion{O}{iii}}	& 4958.92 & 5006.84 & 0.35 \\
	 		\bracket{\ion{N}{i}} 	& 5199.36 & 5201.86 & 0.65 \\
	 		\bracket{\ion{O}{i}} 	& 6300.30 & 6363.67 & 0.33 \\
	 		\bracket{\ion{N}{ii}} 	& 6548.03 & 6583.41 & 0.34 \\
	 		H\,$\alpha$ 	& 6562.30 & -- & -- \\
	 		\bracket{\ion{S}{ii}} 	& 6716.47 & 6730.85 & Free \\
	 		\hline
	 		\hline
	 		\end{tabular}
	 	% 	\begin{tablenotes}
	 	% 	\note Col\,1: Emission line name. Col\,2: Emission line rest-frame wavelength. Col\,3: Doublet rest-frame wavelength for forbidden lines. Col\,4: The fixed ratio of the amplitudes of the lines within a doublet. `Free' indicates the amplitudes of both doublet constituents are fit independently of each other. 
	 	% 	\end{tablenotes}
	 	% \end{threeparttable}
	 	\end{table}

	\subsection{Absorption Line Strengths and Stellar Populations}
		\label{subsec:absorption}
		Due to the lack of calibration observations of Lick/Cassegrain Image Dissector Scanner spectrograph system (hereafter Lick/IDS system; \citealt{Faber1985, Worthey1994}) we use the line index system (LIS) of \citet{Vazdekis2010} instead. This relies on flux calibrations instead of correcting to the continuum shape and wavelength dependent resolution of the Lick/IDS system. We use the index definitions of \citet{Trager1998}, measuring the following indices: G4300, Fe4383, Ca4455, Fe4531, H\,$\beta$, Fe5015, Mg\,b, Fe5270, Fe5335, Fe5406, Fe5709, Fe5782, NaD, TiO1 and TiO2. TiO1 and TiO2 are considered molecular absorption lines and are measured in magnitude units, while all others are atomic and measured in angstroms.

@@

		\subsubsection{Correcting for Stellar Velocity Dispersion}
			We correct for the effect of the different velocity dispersions of the stars which varyingly spread absorption features such that differing fractions of the absorption is outside of the central bandpasses. To do this, we create a best-fitting spectrum (as in the previous step) which is \textit{not} convolved with the best-fitting LOSVD. A given index, $I$, is then measured for both this `unconvolved' spectrum ($I^\text{unc}$) and the convolved best-fitting spectrum ($I^\text{conv}$), and the ratio of these two indices is used as a multiplicative correction factor for the index measured ($I^\text{obs}$), such that the corrected index ($I^\text{corr}$) is given by
			\begin{equation}
				I^\text{corr} \equiv \frac{I^\text{unc}}{I^\text{conv}} I^\text{obs} \, .
			\end{equation}
			These corrected indices are those reported and discussed in the sections below.

@@

	\begin{table*}
		% \centering
	% \begin{threeparttable}
		\caption{Kinematic classifications. Col.\,1: Galaxy name. Col.\,2: $\lambda_\text{R}$ evaluated at $R_\text{e}$. Col.\,3: Ellipticity at $R_\text{e}$. Col.\,4: Misalignment angle between the kinematic and photometric position angles. Col.\,5: Fast-/slow-rotator (FR/SR) classification. Col.\,6: Regular-rotator (RR) or non-regular-rotator (NRR). Col.\,7: Kinematic features. Col.\,8: Kinematic group.}
		\label{tab:classify}
		\begin{tabular}{l c c c c c c c}
			\hline
			\hline
			Galaxy		& $\lambda_\mathrm{R_e}$ & $\epsilon_\text{e}$  & $\Gamma_\text{kin}$ & FR/SR 	& RR/NRR 	& Feature & Group 	\\
			 & & & (deg) \\
			\hline 
			ESO 443-G024 & 0.048 & 0.35 & $-18\pm\leavevmode\phantom{0}2$	& SR & NRR & KDC & c \\
			IC 1459 	& 0.125 & 0.24 & \leavevmode\phantom{0}$-3\pm\leavevmode\phantom{0}1$ & SR & NRR & KDC & c \\
			IC 1531 	& 0.101 & 0.08 & $-54\pm25$	& FR & NRR & LV & a \\
			IC 4296		& 0.034 & 0.03 & \leavevmode\phantom{$-0$}$8\pm12$ & SR &\leavevmode\phantom{N}RR & -- & e \\
			NGC 612 	& 0.655 & 0.36 & \leavevmode\phantom{$-$}$12\pm\leavevmode\phantom{0}6$	& FR &\leavevmode\phantom{N}RR & -- & e \\
			NGC 1316 	& 0.100 & 0.39 & \leavevmode\phantom{$-0$}$6\pm\leavevmode\phantom{0}2$ & FR & NRR & -- & f \\
			NGC 1399 	& 0.090 & 0.12 & $-74\pm\leavevmode\phantom{0}5$ & SR & NRR & LV & a \\
			NGC 3100 	& 0.354 & 0.24 & \leavevmode\phantom{0}$-8\pm\leavevmode\phantom{0}2$ & FR &\leavevmode\phantom{N}RR & -- & e \\
			NGC 3557 	& 0.312 & 0.20 & \leavevmode\phantom{$-$}$16\pm\leavevmode\phantom{0}5$ & FR &\leavevmode\phantom{N}RR & -- & e\\
			NGC 7075 	& 0.068 & 0.04 & \leavevmode\phantom{$-$}$36\pm50$ & SR & NRR & -- & b \\
			PKS 718-34  & 0.159 & 0.17 & \leavevmode\phantom{$-$}$15\pm25$ & FR & NRR & KDC\tnote{a} & b\\
			\hline
			\hline
			\multicolumn{8}{l}{$^{a}$Tentative classification. A higher signal-to-noise ratio (S/N) in the outer regions of the field of view is required for confirmation.}

@@

	We find 4/11, or $(36\pm15)$\%, of our sample galaxies are regular rotators. This compares to 82\% of the Atlas$^\text{3D}$ sample being classified as regular rotators \citep{Krajnovic2011}. However the likely-hood of a given galaxy being a regular rotator is highly mass dependent with the likely-hood decreasing with increasing mass. Thus since our Southern sample are all extremely massive galaxies, we expect to find a higher fraction of non-regular rotators than the Atlas$^\text{3D}$ survey.

	\begin{figure}
		\includegraphics[width=\columnwidth]{lambda_R_ellipticity.png}
		\caption{$\lambda_\mathrm{R_e}$\,--\,ellipticity diagram. VIMOS and MUSE measurements are shown in red and blue, respectively. For comparison, Atlas$^\text{3D}$ galaxies \citep{Emsellem2011} are shown in black and MASSIVE galaxies \citep{Veale2017} in grey. The theoretical limit (edge-on systems) of disc-dominated galaxies is shown in solid magenta, with lines of constant intrinsic angular momentum but varying inclination in dotted magenta. The black solid lines show the limits of the fast-/slow-rotator classes. The MASSIVE survey does not report substructure, so the MASSIVE sample galaxies are shown with filled circles.}
		\label{fig:lambdaR_ellip}
	\end{figure}

@@

	In addition to this, we attempt to identify the kinematic features defined by \citet{Krajnovic2011} in an algorithmic way. However, the artefacts from the VIMOS quadrants confuse ellipse fitting algorithms so only maps derived from the MUSE data are classified in this way; kinematic features in maps derived from the VIMOS data are identified by eye. These classification are listed in Col.\,7 of Table \ref{tab:classify} and the corresponding kinematic group to which a given galaxy belongs to is given is Col.\,8. We observe 3 KDCs (although PKS 718-34 is only a tentative classification) such that $29\pm19$\% of non-regular rotators in our Southern sample definitely (not including PKS 718-34) contain KDCs (or $43\pm19$\% including PKS 718-34), with the large uncertainty reflecting the low-number statistics. This is consistent with the Atlas$^\text{3D}$ survey who found find $25\pm7$\% of non-regular rotators host KDCs \citep{Krajnovic2011}.

% Misaligned systems may appear aligned in certain projections (though aligned systems will be aligned in all projections) and as such $\Gamma_\text{kin}$ cannot be used to describe the intrinsic shape of an individual galaxy, but, as described in Section \ref{sec:ETG}, it can be used in a statistical manner. We find all the regular rotators in our Southern sample, are consistent with having aligned photometry and kinematic position angles to within 11\degree, while non-regular rotators have a large range of values of $\Gamma_\text{kin}$. IC 1531, NGC7075 and PKS 718-34 all have very large uncertainties in the value of $PA_\text{phot}$ due to the VIMOS quadrant artefacts causing the fitting routine of \textsc{kinemetry} to become unreliable.

		% The lack of misalignments in regular rotators is consistent with \citet{Cappellari2007}, \citet{Krajnovic2011} and \citet{Fogarty2015}, who all showed that regular rotators almost always have aligned photometric and kinematic axes with very little scatter and that regular rotators with a significant misalignment are either interacting or strongly barred. The lack of misalignments suggests that the regular rotators (including those within our Southern sample) are consistent with being axisymmetric \citep{Cappellari2016}.

		% Misalignments between the photometric and kinematic position angles are routinely observed for non-regular rotators. This generally implies a more triaxial intrinsic shape, although large misalignments are extremely rarely observed in galaxies with $\epsilon > 0.4$, suggesting that non-regular rotators are more spherical in shape \citep{Cappellari2016}. The non-regular rotators in our Southern sample indeed all have $\epsilon < 0.4$ showing that they are consistent with a fairly spherical, triaxial intrinsic shape.

\section{Absorption Line Strengths and Stellar Populations}
	\label{sec:stellarPop}

>>>>

	\begin{table*}
		\centering
	% \begin{threeparttable}
		\caption{Key sample characteristics of the Southern Sample galaxies. Col.\,1: host galaxy name. Col.\,2: radio source name from Parkes Southern Radio Source Catalogue. We hereafter refer to the last galaxy by its PKS name only. Col.\,3: redshift. Col.\,4: National Radio Astronomy Observatory (NRAO) Very Large Array (VLA) Sky Survey (NVSS) 1.4 GHz flux density \citep{Condon1998}. Col.\,5: Two Micron All Sky Survey (2MASS) $K$-band apparent magnitude (with errors of $\pm 0.025$ mag; \citealt{Skrutskie2006}). Col.\,6: dust morphologies from (a) \citet{Govoni2000}, (b) \citet{Lauer2005}, (c) \citet{Bettoni2001}, (d) \citet{Sandage1979}, (e) \citet{Colbert2001}.}
		\label{tab:sample}
		\begin{tabular}{l c c c c l}
			\hline
			\hline
			Host galaxy	& Radio source 	& Redshift	& $S_\text{1.4\,GHz}$	& $m_K$ & Dust morphology\\
						& (PKS) 		& 			& (mJy) 			& (mag)	&\\
			\hline 
			ESO 443-G024 & 1258-321 	& 0.01703	& $1387 \pm 45$		& 8.51 & no dust\tnote{a}	\\ 
			IC 1459 	& 2254-367 		& 0.00565 	& $1280 \pm 45$		& 6.81 & dust lane\tnote{b}	\\
			IC 1531 	& 0007-325 		& 0.02553 	& \leavevmode\phantom{0}$388 \pm 12$		& 9.55 & --					\\
			IC 4296		& 1333-\leavevmode\phantom{0}33 		& 0.01248 	& $1342 \pm 41$		& 7.50 & edge-on disc\tnote{b} \\
			NGC 612 	& 0131-\leavevmode\phantom{0}36 		& 0.02954 	& \leavevmode\phantom{0}$585 \pm 18$		& 9.58 & dust lane\tnote{c}	\\
			NGC 1316 	& 0320-\leavevmode\phantom{0}37 & 0.00591 	& \leavevmode\phantom{0}$255 \pm 10$		& 5.59 & dust patches\tnote{b} \\
			NGC 1399 	& 0336-\leavevmode\phantom{0}35 & 0.00472 	& \leavevmode\phantom{0}$209 \pm \leavevmode\phantom{0}7$	& 6.31 & no dust\tnote{b}	\\
			NGC 3100 	& 0958-314 		& 0.00879 	& \leavevmode\phantom{0}$530 \pm 16$		& 8.08 & dust lane\tnote{d}	\\
			NGC 3557 	& 1107-372 		& 0.01016 	& \leavevmode\phantom{0}$484 \pm 16$		& 7.20 & face-on disc\tnote{b}\\
			NGC 7075 	& 2128-388 		& 0.01819 	& \leavevmode\phantom{0}$837 \pm 28$		& 9.56 & --					\\
			--			& 0718-\leavevmode\phantom{0}34 		& 0.02897 	& $1119 \pm 41$		& 9.97 & dust patches\tnote{e} \\
			\hline
			\hline
		\end{tabular}
	% 	\begin{tablenotes}
	% 	\footnotesize
	% 	\note Col.\,1: host galaxy name. Col.\,2: radio source name from Parkes Southern Radio Source Catalogue. Col.\,3: redshift. Col.\,4: National Radio Astronomy Observatory (NRAO) Very Large Array (VLA) Sky Survey (NVSS) 1.4 GHz flux density \citep{Condon1998}. Col.\,5: Two Micron All Sky Survey (2MASS) $K$-band apparent magnitude (with errors of $\pm 0.025$ mag; \citealt{Skrutskie2006}). Col.\,6: dust morphologies from (a) \citet{Govoni2000}, (b) \citet{Lauer2005}, (c) \citet{Bettoni2001}, (d) \citet{Sandage1979}, (e) \citet{Colbert2001}. 
	% 	\item We hereafter refer to the last galaxy by its PKS name only.
	% 	\end{tablenotes}
	% \end{threeparttable}
	\end{table*}

@@

	\subsection{Stellar Kinematics}
		\label{subsec:starKin}
		Each bin is fit independently again using \textsc{pPXF} with the MILES library. For the fit, regions around potential emission lines (list below) are masked, and a fourth order polynomial additive continuum correction is used. A Monte--Carlo (MC) estimate of the uncertainties is used.

	\subsection{Ionized Gas Distribution and Kinematics}
		\label{subsec:EmissionLines}
		We fit the ionized gas fluxes and kinematics for the emission lines [\ion{O}{ii}], H$\delta$, H$\gamma$, H$\beta$, [\ion{O}{iii}], [\ion{N}{I}], [\ion{O}{i}], [\ion{N}{ii}], H$\alpha$ and [\ion{S}{ii}] using Gaussian templates. This independently fits emission lines from the interstellar medium (ISM), with a single LOSVDs (again parametrised by the Gaussian parameters $v$, the mean velocity and $\sigma$, the velocity dispersion), independently of the stellar kinematics. In the cases of the [\ion{O}{iii}], [\ion{O}{i}] and [\ion{N}{ii}] doublets, the two components of the doublets are fit with a fixed flux ratio of 1:0.34. The [\ion{N}{i}] doublet has a fixed ratio of 1:0.65 \citep{Safier1992}. The two components of the [\ion{O}{ii}] and [\ion{S}{ii}] doublets are fit independently. To minimize template mismatch, whereby emission lines are erroneously fitted to the edges of badly modeled and thus subtracted absorption features, we follow the method set out in \citet{Sarzi2005}, whereby the stellar component is first fitted as above with masked potential emission line regions, followed by the unmasking and fitting of the [\ion{O}{iii}] doublet which sets the kinematics for all the emission lines and finally the amplitude of the remaining emission lines. %Some of the forbidden emission lines have the ratio of their amplitudes fixed (see Table \ref{tab:EmissionLine}, Col.\,4).

		% \begin{table}
	 % 		% \centering
	 % 	% \begin{threeparttable}
	 % 		\caption{Emission lines considered in the \textsc{pPXF} fits. Col\,1: Emission line name. Col\,2: Emission line rest-frame wavelength. Col\,3: Doublet rest-frame wavelength for forbidden lines. Col\,4: The fixed ratio of the amplitudes of the lines within a doublet. `Free' indicates the amplitudes of both doublet constituents are fit independently of each other.}
	 % 		\label{tab:EmissionLine}
	 % 		\begin{tabular}{l c c c}
	 % 		\hline
	 % 		\hline
	 % 		Emission & Rest-frame & Doublet rest-frame & Amplitude  \\
	 % 		Line & wavelength & wavelength & ratio \\
	 % 		 & (\AA) & (\AA) \\
	 % 		\hline
	 % 		\bracket{\ion{O}{ii}} 	& 3726.03 & 3728.82 & Free \\
	 % 		H$\delta$ 	& 4101.76 & -- & -- \\
	 % 		H$\gamma$ 	& 4340.47 & -- & -- \\
	 % 		H$\beta$ 		& 4861.33 & -- & -- \\
	 % 		\bracket{\ion{O}{iii}}	& 4958.92 & 5006.84 & 0.35 \\
	 % 		\bracket{\ion{N}{i}} 	& 5199.36 & 5201.86 & 0.65 \\
	 % 		\bracket{\ion{O}{i}} 	& 6300.30 & 6363.67 & 0.33 \\
	 % 		\bracket{\ion{N}{ii}} 	& 6548.03 & 6583.41 & 0.34 \\
	 % 		H$\alpha$ 	& 6562.30 & -- & -- \\
	 % 		\bracket{\ion{S}{ii}} 	& 6716.47 & 6730.85 & Free \\
	 % 		\hline
	 % 		\hline
	 % 		\end{tabular}
	 % 	% 	\begin{tablenotes}
	 % 	% 	\note Col\,1: Emission line name. Col\,2: Emission line rest-frame wavelength. Col\,3: Doublet rest-frame wavelength for forbidden lines. Col\,4: The fixed ratio of the amplitudes of the lines within a doublet. `Free' indicates the amplitudes of both doublet constituents are fit independently of each other. 
	 % 	% 	\end{tablenotes}
	 % 	% \end{threeparttable}
	 % 	\end{table}

	\subsection{Absorption Line Strengths}
		\label{subsec:absorption}
		Due to the lack of calibration observations of Lick/Cassegrain Image Dissector Scanner spectrograph system (hereafter Lick/IDS system; \citealt{Faber1985, Worthey1994}) we use the line index system (LIS) of \citet{Vazdekis2010} instead. This relies on flux calibrations instead of correcting to the continuum shape and wavelength dependent resolution of the Lick/IDS system. We use the index definitions of \citet{Trager1998}, measuring the following indices: G4300, Fe4383, Ca4455, Fe4531, H\,$\beta$, Fe5015, Mg\,b, Fe5270, Fe5335, Fe5406, Fe5709, Fe5782, NaD, TiO1 and TiO2. TiO1 and TiO2 are considered molecular absorption lines and are measured in magnitude units, while all others are atomic and measured in angstroms.

@@

		\subsubsection{Correcting for Stellar Velocity Dispersion}
			\label{subsubsec:EmissionFit}
			We correct for the effect of the different velocity dispersions of the stars which varyingly spread absorption features such that differing fractions of the absorption is outside of the central bandpasses. To do this, we create a best-fitting spectrum (as in the previous step) which is \textit{not} convolved with the best-fitting LOSVD. A given index, $I$, is then measured for both this `unconvolved' spectrum ($I^\text{unc}$) and the convolved best-fitting spectrum ($I^\text{conv}$), and the ratio of these two indices is used as a multiplicative correction factor for the index measured ($I^\text{obs}$), such that the corrected index ($I^\text{corr}$) is given by
			\begin{equation}
				I^\text{corr} \equiv \frac{I^\text{unc}}{I^\text{conv}} I^\text{obs} \, .
			\end{equation}
			These corrected indices are those reported and discussed in the sections below.

@@

	\begin{table*}
		\centering
	% \begin{threeparttable}
		\caption{Kinematic classifications. Col.\,1: Galaxy name. Col.\,2: $\lambda_\text{R}$ evaluated at $R_\text{e}$. Col.\,3: Ellipticity at $R_\text{e}$. Col.\,4: Misalignment angle between the kinematic and photometric position angles. Col.\,5: Fast-/slow-rotator (FR/SR) classification. Col.\,6: Regular-rotator (RR) or non-regular-rotator (NRR). Col.\,7: Kinematic features. Col.\,8: Kinematic group.}
		\label{tab:classify}
		\begin{tabular}{l c c c c c c c}
			\hline
			\hline
			Galaxy		& $\lambda_\mathrm{R_e}$ & $\epsilon_\text{e}$  & $\Gamma_\text{kin}$ & FR/SR 	& RR/NRR 	& Feature & Group 	\\
			 & & & (deg) \\
			\hline 
			ESO 443-G024 & 0.048 & 0.35 & $-18\pm\leavevmode\phantom{0}2$	& SR & NRR & KDC & c \\
			IC 1459 	& 0.125 & 0.24 & \leavevmode\phantom{0}$-3\pm\leavevmode\phantom{0}1$ & SR & NRR & KDC & c \\
			IC 1531 	& 0.101 & 0.08 & $-54\pm25$	& FR & NRR & LV & a \\
			IC 4296		& 0.034 & 0.03 & \leavevmode\phantom{$-0$}$8\pm12$ & SR &\leavevmode\phantom{N}RR & -- & e \\
			NGC 612 	& 0.655 & 0.36 & \leavevmode\phantom{$-$}$12\pm\leavevmode\phantom{0}6$	& FR &\leavevmode\phantom{N}RR & -- & e \\
			NGC 1316 	& 0.100 & 0.39 & \leavevmode\phantom{$-0$}$6\pm\leavevmode\phantom{0}2$ & FR & NRR & -- & f \\
			NGC 1399 	& 0.090 & 0.12 & $-74\pm\leavevmode\phantom{0}5$ & SR & NRR & LV & a \\
			NGC 3100 	& 0.354 & 0.24 & \leavevmode\phantom{0}$-8\pm\leavevmode\phantom{0}2$ & FR &\leavevmode\phantom{N}RR & -- & e \\
			NGC 3557 	& 0.312 & 0.20 & \leavevmode\phantom{$-$}$16\pm\leavevmode\phantom{0}5$ & FR &\leavevmode\phantom{N}RR & -- & e\\
			NGC 7075 	& 0.068 & 0.04 & \leavevmode\phantom{$-$}$36\pm50$ & SR & NRR & -- & b \\
			PKS 718-34  & 0.159 & 0.17 & \leavevmode\phantom{$-$}$15\pm25$ & FR & NRR & KDC\tnote{a} & b\\
			\hline
			\hline
			\multicolumn{8}{l}{$^{a}$Tentative classification. A higher signal-to-noise ratio (S/N) in the outer regions of the field of view is required for confirmation.}

@@

	\subsection{Regular/Non-regular Rotators}
		We find 4/11, or $(36\pm15)$\%, of our sample galaxies are regular rotators. This compares to 82\% of the Atlas$^\text{3D}$ sample being classified as regular rotators \citep{Krajnovic2011}. However the likely-hood of a given galaxy being a regular rotator is highly mass dependent with the likely-hood decreasing with increasing mass. Thus since our Southern sample are all extremely massive galaxies, we expect to find a higher fraction of non-regular rotators than the Atlas$^\text{3D}$ survey.

	\subsection{Fast/Slow Rotators}
		\begin{figure}
			\includegraphics[width=\columnwidth]{lambda_R_ellipticity.png}
			\caption{$\lambda_\mathrm{R_e}$\,--\,ellipticity diagram. VIMOS and MUSE measurements are shown in red and blue, respectively. For comparison, Atlas$^\text{3D}$ galaxies \citep{Emsellem2011} are shown in black and MASSIVE galaxies \citep{Veale2017} in grey. The theoretical limit (edge-on systems) of disc-dominated galaxies is shown in solid magenta, with lines of constant intrinsic angular momentum but varying inclination in dotted magenta. The black solid lines show the limits of the fast-/slow-rotator classes. The MASSIVE survey does not report substructure, so the MASSIVE sample galaxies are shown with filled circles.}
			\label{fig:lambdaR_ellip}
		\end{figure}

@@

	\subsection{Kinematic Features}
		In addition to this, we attempt to identify the kinematic features defined by \citet{Krajnovic2011} in an algorithmic way. However, the artefacts from the VIMOS quadrants confuse ellipse fitting algorithms so only maps derived from the MUSE data are classified in this way; kinematic features in maps derived from the VIMOS data are identified by eye. These classification are listed in Col.\,7 of Table \ref{tab:classify} and the corresponding kinematic group to which a given galaxy belongs to is given is Col.\,8. We observe 3 KDCs (although PKS 718-34 is only a tentative classification) such that $29\pm19$\% of non-regular rotators in our Southern sample definitely (not including PKS 718-34) contain KDCs (or $43\pm19$\% including PKS 718-34), with the large uncertainty reflecting the low-number statistics. This is consistent with the Atlas$^\text{3D}$ survey who found find $25\pm7$\% of non-regular rotators host KDCs \citep{Krajnovic2011}.

	\subsection{Intrinsic Shape}
		The misalignment angle between the photometric and kinematic position angle is given in Col.\,4 of Table \ref{tab:classify}. Misaligned systems may appear aligned in certain projections, but though aligned systems will be aligned in all projections, and a low value of $\Gamma_\text{kin}$ cannot be used to describe the intrinsic shape of an individual galaxy, but it can be interpreted within a statistical framework. However, a high value of $\Gamma_\text{kin}$ can give an insight into the intrinsic shape of an individual galaxy. We find all the regular rotators in our Southern sample, are consistent with having aligned photometry and kinematic position angles to within 11\degr, while non-regular rotators have a large range of values of $\Gamma_\text{kin}$. IC 1531, NGC7075 and PKS 718-34 all have very large uncertainties in the value of $PA_\text{phot}$ due to the VIMOS quadrant artefacts causing the fitting routine of \textsc{kinemetry} to become unreliable.

		The lack of misalignments in regular rotators is consistent with \citet{Cappellari2007}, \citet{Krajnovic2011} and \citet{Fogarty2015}, who all showed that regular rotators almost always have aligned photometric and kinematic axes with very little scatter and that regular rotators with a significant misalignment are either interacting or strongly barred. The lack of misalignments suggests that the regular rotators (including those within our Southern sample) are consistent with being axisymmetric \citep{Cappellari2016}.

		Misalignments between the photometric and kinematic position angles are routinely observed for non-regular rotators. This generally implies a more triaxial intrinsic shape, although large misalignments are extremely rarely observed in galaxies with $\epsilon > 0.4$, suggesting that non-regular rotators are more spherical in shape \citep{Cappellari2016}. The non-regular rotators in our Southern sample indeed all have $\epsilon < 0.4$ showing that they are consistent with a fairly spherical, triaxial intrinsic shape.

\section{Absorption Line Strengths}
	\label{sec:absorption}
	Using the methods described in Section \ref{subsec:absorption} we produce maps of the absorption line strength indices for each galaxy (shown in Appendix \ref{sec:Maps}). Here we measure the Mg\,--\,velocity dispersion relation and compare our absorption line strength measurements to the literature.

	\subsection{Mg\,--\,$\sigma$ relation}
		\label{subsec:Mgsigma}
		The Mg$_2$ absorption line index of \citet{Trager1998} has overlapping bandpasses with the Mg\,b index (also of \citeauthor{Trager1998}), but includes the MgH molecular absorption line, and is hence considered a molecular index and is measured in units of magnitude. \citet{Bender1993} observed the tight relationship between the global Mg$_2$ absorption line strength and logarithm of the central velocity dispersion, $\sigma_0$, in elliptical galaxies. They also noticed that residuals to the linear best-fitting appeared to be intrinsic as they have a near Gaussian shape about the median values, but do not seem to be correlated to any other galaxy property.

		Since part of the red continuum band of the Mg$_2$ index is outside of the spectral range of VIMOS, we instead use the Mg\,b index. \citet{Ziegler1997} show there is an approximately linear relationship between Mg\,b and Mg$_2$, with a gradient of 14.3--15.5\,mag\,\AA$^{-1}$\ depending on metallicity. We thus use Mg\,b as a proxy for Mg$_2$.

		Using an aperture with a radius of 2 arcsec on each datacube, we measure $\sigma_0$ and Mg\,b at a spectral resolution of 8.4\,\AA\ full-width half-maximum (FWHM), chosen such that the transformation functions of \citet{Vazdekis2010} can be used to change the literature measurements from the Lick/IDS system to the LIS. The results are shown in Fig.\,\ref{fig:globalMg} with the best-fitting linear relationship (found using \textsc{lts\_linefit} by \citealt{Cappellari2013}) shown by the solid black line. This has a gradient of $2.3 \pm 0.5 \,\mathrm{\AA\,dex^{-1}}$) and intrinsic scatter of $0.13 \pm 0.10 \, \mathrm{\AA}$. %Individual measurements for each galaxy are given in table \ref{tab:globalMg}.
		This is in very good agreement with the gradient found by \citet{Ziegler1997} for a sample of elliptical galaxies within Virgo and Coma using data from \citet{Dressler1987} of $2.5\,\mathrm{\AA\,dex^{-1}}$ (blue dotted line in Fig.\,\ref{fig:globalMg}), with an intrinsic scatter of 0.16\,\AA\ for galaxies with $\log \sigma_0 \geqslant 2.3$.

		\begin{figure}
			\includegraphics[width=\columnwidth]{Mg_sigma.png}
			\caption[Global Mg\,b\,--\,$\sigma$]{The Mg\,b\,--\,velocity dispersion relation using a 2\arcsec aperture. We find a similar gradient to our best-fitting (solid) as that found by \citet[; dotted line]{Ziegler1997}.}
			\label{fig:globalMg}
		\end{figure}

	\subsection{Comparison to the Literature}
		\label{subsec:Lit}
		Given that there is no well defined list of corrections (and methods) that is universally followed, care must be taken when making comparisons to the literature. When comparing to a particular paper we correct for the same effects described in the paper, but using our methods, as described in Section \ref{subsec:Absorption}. As in Section \ref{subsec:Mgsigma} we use a resolution of 8.4\,\AA\ FWHM in order to use the transformation function provided by \citet{Vazdekis2010} from Lick/IDS system to the LIS.
